Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-30 papers/ms.tex
update ms

\subsection{Is CH-2 real?}
\label{subsec:ch2}

@@

Given its low density, in CH-2 really a star cluster?  For this
discussion, we adopt the definition that a star cluster is a group of
at least 12 stars that was physically associated at its time of
formation.  The ``12'' is set to distinguish star clusters from
high-order multiples \citep[see][]{krumholz_star_2019}.  We explicitly
do not require a ``star cluster'' to be gravitationally bound:
dissolved clusters as well as their tidal tails are included in our
adopted definition of ``clusters''.  We similarly do not require a
threshold number of stars per unit spatial volume.  The latter point
acknowledges that an important factor in cluster identification is
also density in velocity space.  Perhaps once stellar rotation periods
and chemical abundances reach the same level of ubiquity as stellar
proper motions, they might enable further refinement of our ability to
discover stars that formed as part of the same event.

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as well as through the
expansion itself \citep[see][]{crundall_chronostar_2019}.  A more
minimal approach is that suggested by \citet{tofflemire_2021}: search
for coeval, phase-space neighbors, measure their ages, and determine
if they share a common age.  This approach can demonstrate whether a
star is currently associated with a set of coeval stars, though it
falls short of determining what the association looked like in the
past.  Our analysis of CH-2 meets the latter standard for the
existence of a $\approx$40\,Myr stellar association.  It would be a
worthy exercise for future work to perform a similar search for coeval
phase-space neighbors on the entire dataset of known exoplanet hosts.
For the time being, we can offer the anecdotal point that in our
experience, most stars do not have dozens of 40\,Myr neighbors within
a local volume of a few \kms\ and tens of parsecs.

>>>>

\subsection{Is CH-2 a Coeval Population?}
\label{subsec:ch2}

@@

Given its low density, in CH-2 a real star cluster?  For this
discussion, we adopt the definition that a star cluster is a group of
at least 12 stars that was physically associated at its time of
formation.  The ``12'' is set to distinguish star clusters from
high-order multiples \citep[see][]{krumholz_star_2019}.  We explicitly
do not require a ``star cluster'' to be gravitationally bound:
dissolved clusters as well as their tidal tails are included in our
adopted definition of ``clusters''.  We similarly do not require a
threshold number of stars per unit spatial volume.  The latter point
acknowledges that an important factor in cluster identification is
also density in velocity space.  Perhaps once stellar rotation periods
and chemical abundances reach the same level of ubiquity as stellar
proper motions, they might enable further refinement of our ability to
discover stars that formed as part of the same event.

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as well as through the
expansion itself \citep[see][]{crundall_chronostar_2019}.  A more
minimal approach is that suggested by \citet{tofflemire_2021}: search
for coeval, phase-space neighbors, measure their ages, and determine
if they share a common age.  This approach can demonstrate whether a
star is currently associated with a set of coeval stars, though it
falls short of determining what the association looked like in the
past.  While our analysis of CH-2 meets the latter standard for
demonstrating the
existence of a $\approx$40\,Myr stellar association, it does not meet
the standard of demonstrating that its stars were associated at birth. 
It would be a worthy exercise for future work to perform a similar
search for coeval phase-space neighbors on the entire dataset of known
exoplanet hosts.  For the time being, we can offer the anecdotal point
that in our experience, most stars do not have dozens of 40\,Myr
neighbors within a local volume of a few \kms\ and tens of parsecs.
